\documentclass{article}
\usepackage{fullpage}
\usepackage{graphicx}
\title{Decision and RAID Logs}
\author{Engineers for Exploration, UC San Diego}
\begin{document}
\maketitle
\begin{enumerate}
    \item Slide: Why do we need to keep track of decisions?
    \begin{itemize}
        \item Get buy in from everyone
        \begin{itemize}
            \item Projects are collaborative
            \item Everyone has distinct perspectives and interests
            \item Building trust and confidence
            \item Slows down decision making
        \end{itemize}
        \item Remember why we did something in the future
        \begin{itemize}
            \item Captures nuance, impacts, context
            \item Allows for continuous improvement and retrospectives
        \end{itemize}
        \item Communicate decisions to the rest of the team
    \end{itemize}
    \item Slide: What kinds of decisions do we log?
    \begin{itemize}
        \item Critical decisions
        \begin{itemize}
            \item Things with massive impacts
        \end{itemize}
        \item Course of action decisions
        \begin{itemize}
            \item Understanding why the project chose to go one way or another
        \end{itemize}
        \item Risk management decisions
        \begin{itemize}
            \item Enumerate all risks
            \item Roadmap for handling uncertainties and unforseen challenges
        \end{itemize}
        \item Project team decisions
        \begin{itemize}
            \item choices made regarding team composition, responsibilities and communication protocols
        \end{itemize}
        \item Deliverables decisions
        \begin{itemize}
            \item  what to deliver, when and how are critical for meeting project objectives.
            \item insight into the rationale behind deliverable choices and serving as a reference for future projects with similar objectives
        \end{itemize}
        \item Metrics and evaluation decisions
        \begin{itemize}
            \item ensures that the project team is aligned on the metrics that matter and facilitates data-driven decision-making
            \item selection of key performance indicators (KPIs), evaluation methodologies and success criteria find a home in the decision log
        \end{itemize}
    \end{itemize}
    \item Slide: What do we log?
    \begin{itemize}
        \item Decision details
        \begin{itemize}
            \item who/what/when/where
            \item Potential impacts
            \item Potential solutions
        \end{itemize}
        \item Decision maker
        \begin{itemize}
            \item Clarity on who holds the decision-making reins is crucial for accountability and ensures that there's no ambiguity about who owns the outcome of the decision.
        \end{itemize}
        \item Stakeholders involved
        \begin{itemize}
            \item include the names/roles of the people directly impacted by the decision.
        \end{itemize}
        \item Rationale
        \begin{itemize}
            \item `why' behind a decision is perhaps the most critical aspect. Document the thought processes, considerations and factors that contributed to the final choice
        \end{itemize}
        \item Follow-up actions
        \begin{itemize}
            \item Outline the course of action that follows each decision. This may include specific tasks, milestones, or actions that need to be taken based on the chosen path.
        \end{itemize}
    \end{itemize}
    \item Slide: What is a RAID log?
    \begin{itemize}
        \item Risks
        \item Assumptions
        \item Issues
        \item Dependencies
        \item Actions
        \item Decisions
    \end{itemize}
\end{enumerate}
\end{document}